---
title: "FACSresponseBFP"
author: "Edwin Eliasson"
date: "10/14/2021"
output: html_document
---

## Load libraries
```{r, echo=FALSE}
library(flowCore)
library(tidyverse)
library(viridis)
library(hrbrthemes)
library(hexbin)
```

## Set working directory 
```{r,warning=FALSE}
setwd("/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/Facs/Data analysis/data/FACS_2021_09_09_CSV/")
```

## Load data

#All data is in csv format in the "../data/2021-08-27_at_08-43-55am" folder
```{r,warning=FALSE}
filenames = list.files(path = "../data/FACS_2021_09_09_CSV/Sample Group - 1 - Gate A/",full.names = T)

# Extract plate position from filename
sample_name = filenames %>% gsub("_Data Source - 1_A.csv","",.) %>% gsub("le_Group_1_","",.) %>% gsub(".*am.","",.)


# Loop through and merge all files into a big tibble
tbl = tibble()
for (i in 1:length(filenames)) {
  tbl_file = fread(filenames[i]) %>% mutate(POS = sample_name[i])
  tbl = rbind(tbl,tbl_file)
}

rm(tbl_file)
```

## Pre-procesing

#Replacement of hypgen (-) in columns & removal of defected index column
```{r}

names(tbl) <- gsub("\\-",".", names(tbl))
names(tbl) <- gsub("\\.A.Compensated","", names(tbl))
names(tbl) <- gsub("\\Pacific Blue","BFP", names(tbl))
tbl$Index = NULL

glimpse(tbl)
```


## Filter out cells with negative intensity and log transform
```{r}

tbl =
  tbl %>%
  filter(EGFP > 0) %>%
  mutate(log_EGFP = log10(EGFP+1)) %>%
  filter(miRFP670 > 0) %>% 
  mutate(log_miRFP670 = log10(miRFP670+1)) %>%
  filter(BFP > 0) %>%
  mutate(log_BFP = log10(BFP+1))
  
head(tbl)
```

#Add index for cell
```{r}
tbl <- tbl %>% mutate(cell_id = 1:nrow(tbl))
```



#Convert into tidy tibble and add channel info
```{r}
tbl_tidy =
  tbl %>% 
  pivot_longer(-c(POS,TIME,cell_id),names_to = "CHANNEL",values_to = "INTENSITY") 
  #mutate(SCALE = ifelse(grepl("Lin",CHANNEL),"lin","log")) %>% 
  
glimpse(tbl_tidy)
```

#Format meta data
```{r}
tbl_meta = 
  fread(file = "../data/plate_map.csv") %>% 
  mutate(DOSE = as.character(DOSE)) %>% 
  mutate(DOSE_1 = as.character(DOSE_1)) %>% 
  mutate(DOSE_2 = as.character(DOSE_2)) %>%
  mutate(DOSE_3 = as.character(DOSE_3))
```


#Merge meta data with FACS meta data
```{r}
tbl_tidy =
  tbl_tidy %>% 
  full_join(tbl_meta,by = "POS")

head(tbl_tidy)
```

#Matrix with flipped columns
```{r}
tbl_red_green_blue =

tbl_tidy %>% 
  filter(CHANNEL %in% c("log_EGFP", "log_miRFP670","log_BFP")) %>% 
  pivot_wider(names_from = CHANNEL, values_from = INTENSITY)

glimpse(tbl_red_green_blue)
```

### Single plasmid TETON ###

#TetON violin plot, log scale
```{r,fig.width=8,fig.height=5}

p_violoin_tet_BFP =
tbl_tidy %>% 
  filter(STRAIN %in% c("Tet")) %>% 
  filter(NUM.IND %in% c("1")) %>% 
  filter(CHANNEL %in% c("log_BFP")) %>% 
  ggplot(aes(x = DOSE_1,y = INTENSITY,group = DOSE_1, fill = DOSE_1)) +
  geom_violin(alpha = 0.5, adjust = 0.0001,draw_quantiles = 0.5) +
  scale_color_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM)", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  stat_compare_means(ref.group = "0",label = "p.signif") +
  ggtitle("Violin plot of BFP - Tetracyclin plasmid") +
  xlab("Tetracyclin (µM)") +
  ylab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_violoin_tet_BFP
```

#BFP expression depending of Tetracyclin conc.
```{r}
p_density_tet_BFP_diff_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet")) %>% 
  ggplot(aes(log_BFP, color = DOSE_1, fill = DOSE_1)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  facet_wrap(vars(DOSE_1, INDUCER_1),nrow = 2) +
  scale_color_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  ggtitle ("Density plots for BFP expression - Tetracyclin plasmid") +
  ylab("Density") + 
  xlab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_tet_BFP_diff_plot

```

#RFP expression depending of Tetracyclin conc.in ONE plot
```{r}
p_density_tet_BFP_same_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet")) %>% 
  ggplot(aes(log_BFP, color = DOSE_1, fill = DOSE_1)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  
  scale_color_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  ggtitle ("Density plots for BFP expression - Tetracyclin plasmid") +
  ylab("Density") + 
  xlab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_tet_BFP_same_plot

```

LINCOLN GFP expression depending of EST
```{r}
p_density_tet_BFP_lincoln =
 tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet")) %>% 
  ggplot(lincoln_weather, mapping = aes(x = log_BFP, y = DOSE_1, fill = stat(x))) +
  geom_density_ridges_gradient(scale = 3, rel_min_height = 0.01) +
  scale_fill_viridis_c(name = "Expression", option = "magma") +
  theme_bw() +
  ggtitle("Density plots for BFP expression - Tetracyclin plasmid") +
  ylab("DOSE (µM)") +
  xlab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5,face = "bold", size = 15))

p_density_tet_BFP_lincoln

```



### Double plasmid Tetracycline & Estradiol ###


#BFP & GFP violin expression
```{r}
p_violin_Tet.est_BFP_GFP =

tbl_tidy %>% 
  filter(STRAIN %in% c("Tet.Est")) %>%
  filter(NUM.IND %in% c("2")) %>% 
  filter(CHANNEL %in% c("log_BFP","log_EGFP")) %>% 
  
  ggplot(aes(x = DOSE,y = INTENSITY,group = DOSE, fill = DOSE)) +
  geom_violin(alpha = 0.5, adjust = 0.0001,draw_quantiles = 0.5) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Est",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Est", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  stat_compare_means(ref.group = "0",label = "p.signif") +
  ggtitle("Violin plot of BFP & GFP intensity -
Tetracyclin & Estradiol plasmids") +
  facet_wrap(vars(CHANNEL, STRAIN)) +
  xlab("Tetracyclin and Estradiol (µM)") +
  ylab("Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_violin_Tet.est_BFP_GFP

```

#BFP expression depending of TET conc.
```{r}
p_density_Tet.est_BFP_all_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Est")) %>% 
  #mutate(DOSE_1 = factor(DOSE_1,levels = c("0","100","500","1000"),ordered = TRUE)) %>%
  ggplot(aes(log_BFP, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  facet_wrap(vars(DOSE),nrow = 1) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Est",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Est", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for BFP expression -
Tetracyclin & Estradiol plasmids") +
  ylab("Density") + 
  xlab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.est_BFP_all_plot 
```

BFP expression depending of Tet conc.
```{r}
p_density_Tet.est_BFP_same_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Est")) %>% 
  #mutate(DOSE_1 = factor(DOSE_1,levels = c("0","100","500","1000"),ordered = TRUE)) %>%
  ggplot(aes(log_BFP, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  #facet_wrap(vars(DOSE),nrow = 3) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Est",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Est", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for BFP expression -
Tetracyclin & Estradiol plasmids") +
  ylab("Density") + 
  xlab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.est_BFP_same_plot 
```


LINCOLN BFP expression depending of 
```{r}
p_density_Tet.est_BFP_lincoln =
 tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Est")) %>% 
  ggplot(lincoln_weather, mapping = aes(x = log_BFP, y = DOSE, fill = stat(x))) +
  geom_density_ridges_gradient(alpha = 0.1, adjust = 0.0001, scale = 3, rel_min_height = 0.01)  +
  scale_fill_viridis_c(name = "Expression", option = "magma") +
  theme_bw() +
  ggtitle("Density plots for BFP expression -
Tetracyclin & Estradiol plasmids") +
  ylab("DOSE (µM)") +
  xlab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5,face = "bold", size = 15))

p_density_Tet.est_BFP_lincoln
```

## GFP ##

#GFP expression depending of EST conc.
```{r}
p_density_Tet.est_GFP_all_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Est")) %>% 
  #mutate(DOSE_1 = factor(DOSE_1,levels = c("0","100","500","1000"),ordered = TRUE)) %>%
  ggplot(aes(log_EGFP, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  facet_wrap(vars(DOSE),nrow = 1) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Est",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Est", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for GFP expression -
Tetracyclin & Estradiol plasmids") +
  ylab("Density") + 
  xlab("GFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.est_GFP_all_plot 
```


GFP expression depending of EST conc.
```{r}
p_density_Tet.est_GFP_same_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Est")) %>% 
  
  ggplot(aes(log_EGFP, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Est",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Est", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for GFP expression -
Tetracyclin & Estradiol plasmids") +
  ylab("Density") + 
  xlab("GFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.est_GFP_same_plot 
```


LINCOLN GFP expression depending of 
```{r}
p_density_Tet.est_GFP_lincoln =
 tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Est")) %>% 
  ggplot(lincoln_weather, mapping = aes(x = log_EGFP, y = DOSE, fill = stat(x))) +
  geom_density_ridges_gradient(alpha = 0.1, adjust = 0.0001, scale = 3, rel_min_height = 0.01)  +
  scale_fill_viridis_c(name = "Expression", option = "magma") +
  theme_bw() +
  ggtitle("Density plots for GFP expression -
Tetracyclin & Estradiol plasmids") +
  ylab("DOSE (µM)") +
  xlab("GFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5,face = "bold", size = 15))

p_density_Tet.est_GFP_lincoln
```





### Double plasmid Tetracycline & Copper ###


#BFP & RFP violin expression
```{r}
p_violin_Tet.cup_BFP_RFP =

tbl_tidy %>% 
  filter(STRAIN %in% c("Tet.Cup")) %>%
  filter(NUM.IND %in% c("2")) %>% 
  filter(CHANNEL %in% c("log_BFP","log_miRFP670")) %>% 
  
  ggplot(aes(x = DOSE,y = INTENSITY,group = DOSE, fill = DOSE)) +
  geom_violin(alpha = 0.5, adjust = 0.0001,draw_quantiles = 0.5) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Cup",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Cup", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  stat_compare_means(ref.group = "0",label = "p.signif") +
  ggtitle("Violin plot of BFP & RFP intensity -
Tetracyclin & Copper plasmids") +
  facet_wrap(vars(CHANNEL, STRAIN)) +
  xlab("Tetracyclin and Copper (µM)") +
  ylab("Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_violin_Tet.cup_BFP_RFP

```

#BFP expression depending of Tet conc.
```{r}
p_density_Tet.cup_BFP_all_plots =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup")) %>% 
  ggplot(aes(log_BFP, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  facet_wrap(vars(DOSE),nrow = 1) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Cup",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Cup", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for BFP expression -
Tetracyclin & Copper plasmids") +
  ylab("Density") + 
  xlab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.cup_BFP_all_plots 
```

BFP expression depending of Tet conc.
```{r}
p_density_Tet.cup_BFP_same_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup")) %>% 
  #mutate(DOSE_1 = factor(DOSE_1,levels = c("0","100","500","1000"),ordered = TRUE)) %>%
  ggplot(aes(log_BFP, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  #facet_wrap(vars(DOSE),nrow = 3) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Cup",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Cup", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for BFP expression -
Tetracyclin & Copper plasmids") +
  ylab("Density") + 
  xlab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.cup_BFP_same_plot 
```


LINCOLN BFP expression depending of 
```{r}
p_density_Tet.cup_BFP_lincoln =
 tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup")) %>% 
  ggplot(lincoln_weather, mapping = aes(x = log_BFP, y = DOSE, fill = stat(x))) +
  geom_density_ridges_gradient(alpha = 0.1, adjust = 0.0001, scale = 3, rel_min_height = 0.01)  +
  scale_fill_viridis_c(name = "Expression", option = "magma") +
  theme_bw() +
  ggtitle("Density plots for BFP expression -
Tetracyclin & Copper plasmids") +
  ylab("DOSE (µM)") +
  xlab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5,face = "bold", size = 15))

p_density_Tet.cup_BFP_lincoln
```


## RFP ##

#RFP expression depending of CUP conc.
```{r}
p_density_Tet.cup_RFP_all_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup")) %>% 

  ggplot(aes(log_miRFP670, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  facet_wrap(vars(DOSE),nrow = 1) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Cup",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Cup", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for RFP expression -
Tetracyclin & Copper plasmids") +
  ylab("Density") + 
  xlab("RFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.cup_RFP_all_plot 
```


GFP expression depending of Tet conc.
```{r}
p_density_Tet.cup_RFP_same_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup")) %>% 
  
  ggplot(aes(log_miRFP670, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Cup",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Cup", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for RFP expression -
Tetracyclin & Copper plasmids") +
  ylab("Density") + 
  xlab("RFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.cup_RFP_same_plot 
```


LINCOLN GFP expression depending of 
```{r}
p_density_Tet.cup_RFP_lincoln =
 tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup")) %>% 
  ggplot(lincoln_weather, mapping = aes(x = log_miRFP670, y = DOSE, fill = stat(x))) +
  geom_density_ridges_gradient(alpha = 0.1, adjust = 0.0001, scale = 3, rel_min_height = 0.01)  +
  scale_fill_viridis_c(name = "Intesity (a.u.)", option = "magma") +
  theme_bw() +
  ggtitle("Density plots for RFP expression -
Tetracyclin & Copper plasmids") +
  ylab("DOSE (µM)") +
  xlab("RFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5,face = "bold", size = 15))

p_density_Tet.cup_RFP_lincoln
```




###### Three plasmids ########3



#BFP & RFP & GFP violin expression
```{r}
p_violin_Tet.cup.est =

tbl_tidy %>% 
  filter(STRAIN %in% c("Tet.Cup.Est")) %>%
  filter(NUM.IND %in% c("3")) %>% 
  filter(CHANNEL %in% c("log_BFP","log_EGFP", "log_miRFP670")) %>% 
  mutate(DOSE = factor(DOSE, levels = c("0/0/0", "0.5/500/0.005", "1/500/0.01"))) %>% 
  ggplot(aes(x = DOSE,y = INTENSITY,group = DOSE, fill = DOSE)) +
  geom_violin(alpha = 0.5, adjust = 0.0001,draw_quantiles = 0.5) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Cup/Est",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Cup/Est", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  #stat_compare_means(ref.group = "0",label = "p.signif") +
  ggtitle("Violin plot of BFP, GFP & RFP intensity -
Tetracyclin & Copper plasmids") +
  facet_wrap(vars(CHANNEL, STRAIN)) +
  xlab("Tetracyclin, Estradiol & Copper (µM)") +
  ylab("Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_violin_Tet.cup.est

```


#### BFP ###

#BFP expression depending of Tet conc.
```{r}
p_density_Tet.cup.est_BFP_all_plots =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup.Est")) %>% 
  mutate(DOSE = factor(DOSE, levels = c("0/0/0", "0.5/500/0.005", "1/500/0.01"))) %>% 
  ggplot(aes(log_BFP, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  facet_wrap(vars(DOSE),nrow = 1) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Cup/Est",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Cup/Est", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for BFP expression -
Tetracyclin, Estradiol & Copper plasmids") +
  ylab("Density") + 
  xlab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.cup.est_BFP_all_plots 
```

#BFP expression depending of Tet conc.
```{r}
p_density_Tet.cup.est_BFP_same_plots =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup.Est")) %>% 
  mutate(DOSE = factor(DOSE, levels = c("0/0/0", "0.5/500/0.005", "1/500/0.01"))) %>% 
  ggplot(aes(log_BFP, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  #facet_wrap(vars(DOSE),nrow = 1) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Cup/Est",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Cup/Est", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for BFP expression -
Tetracyclin, Estradiol & Copper plasmids") +
  ylab("Density") + 
  xlab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.cup.est_BFP_same_plots 
```


LINCOLN BFP expression depending of 
```{r}
p_density_Tet.cup.est_BFP_lincoln =
 tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup.Est")) %>% 
   mutate(DOSE = factor(DOSE, levels = c("0/0/0", "0.5/500/0.005", "1/500/0.01"))) %>% 
  ggplot(lincoln_weather, mapping = aes(x = log_BFP, y = DOSE, fill = stat(x))) +
  geom_density_ridges_gradient(alpha = 0.1, adjust = 0.0001, scale = 3, rel_min_height = 0.01)  +
  scale_fill_viridis_c(name = "Intesity (a.u.)", option = "magma") +
  theme_bw() +
  ggtitle("Density plots for BFP expression -
Tetracyclin, Estradiol & Copper plasmids") +
  ylab("DOSE (µM)") +
  xlab("BFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5,face = "bold", size = 15))

p_density_Tet.cup.est_BFP_lincoln
```


### RFP ###



#RFP expression depending of CUP conc.
```{r}
p_density_Tet.cup.est_RFP_all_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup.Est")) %>% 
  mutate(DOSE = factor(DOSE, levels = c("0/0/0", "0.5/500/0.005", "1/500/0.01"))) %>% 
  ggplot(aes(log_miRFP670, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  facet_wrap(vars(DOSE),nrow = 1) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Cup/Est",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Cup/Est", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for RFP expression -
Tetracyclin, Estradiol & Copper plasmids") +
  ylab("Density") + 
  xlab("RFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.cup.est_RFP_all_plot 
```


RFP expression depending of Tet conc.
```{r}
p_density_Tet.cup.est_RFP_same_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup.Est")) %>% 
  mutate(DOSE = factor(DOSE, levels = c("0/0/0", "0.5/500/0.005", "1/500/0.01"))) %>% 
  ggplot(aes(log_miRFP670, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Cup/Est",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Cup/Est", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for RFP expression -
Tetracyclin, Estradiol & Copper plasmids") +
  ylab("Density") + 
  xlab("RFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.cup.est_RFP_same_plot 
```


LINCOLN RFP expression depending of 
```{r}
p_density_Tet.cup.est_RFP_lincoln =
 tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup.Est")) %>% 
  mutate(DOSE = factor(DOSE, levels = c("0/0/0", "0.5/500/0.005", "1/500/0.01"))) %>% 
  ggplot(lincoln_weather, mapping = aes(x = log_miRFP670, y = DOSE, fill = stat(x))) +
  geom_density_ridges_gradient(alpha = 0.1, adjust = 0.0001, scale = 3, rel_min_height = 0.01)  +
  scale_fill_viridis_c(name = "Intesity (a.u.)", option = "magma") +
  theme_bw() +
  ggtitle("Density plots for RFP expression -
Tetracyclin, Estradiol & Copper plasmids") +
  ylab("DOSE (µM)") +
  xlab("RFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5,face = "bold", size = 15))

p_density_Tet.cup.est_RFP_lincoln
```



### GFP ###



#GFP expression depending of EST conc.
```{r}
p_density_Tet.cup.est_GFP_all_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup.Est")) %>% 
  mutate(DOSE = factor(DOSE, levels = c("0/0/0", "0.5/500/0.005", "1/500/0.01"))) %>%
  ggplot(aes(log_EGFP, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  facet_wrap(vars(DOSE),nrow = 1) +
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Cup/Est",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Cup/Est", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for GFP expression -
Tetracyclin, Estradiol & Copper plasmids") +
  ylab("Density") + 
  xlab("GFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.cup.est_GFP_all_plot 
```


GFP expression depending of EST conc.
```{r}
p_density_Tet.cup.est_GFP_same_plot =
  tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup.Est")) %>% 
  mutate(DOSE = factor(DOSE, levels = c("0/0/0", "0.5/500/0.005", "1/500/0.01"))) %>%
  ggplot(aes(log_EGFP, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  
  scale_color_viridis(name = "DOSE (µM), 
  Tet/Cup/Est",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM), 
  Tet/Cup/Est", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  
  theme_bw() +
  ggtitle ("Density plots for GFP expression -
Tetracyclin, Estradiol & Copper plasmids") +
  ylab("Density") + 
  xlab("GFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_Tet.cup.est_GFP_same_plot 
```


LINCOLN GFP expression depending of 
```{r}
p_density_Tet.cup.est_GFP_lincoln =
 tbl_red_green_blue %>% 
  filter(STRAIN == c("Tet.Cup.Est")) %>% 
  mutate(DOSE = factor(DOSE, levels = c("0/0/0", "0.5/500/0.005", "1/500/0.01"))) %>%
  ggplot(lincoln_weather, mapping = aes(x = log_EGFP, y = DOSE, fill = stat(x))) +
  geom_density_ridges_gradient(alpha = 0.1, adjust = 0.0001, scale = 3, rel_min_height = 0.01)  +
  scale_fill_viridis_c(name = "Intesity (a.u.)", option = "magma") +
  theme_bw() +
  ggtitle("Density plots for GFP expression -
Tetracyclin, Estradiol & Copper plasmids") +
  ylab("DOSE (µM)") +
  xlab("GFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5,face = "bold", size = 15))

p_density_Tet.cup.est_GFP_lincoln
```



```{r}


p_violoin_tet_BFP
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="violoin_tet_BFP.png")

p_density_tet_BFP_diff_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_tet_BFP_diff_plot.png")

p_density_tet_BFP_same_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_tet_BFP_same_plot.png")

p_density_tet_BFP_lincoln
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_tet_BFP_lincoln.png")

p_violin_Tet.est_BFP_GFP
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="violin_Tet.est_BFP_GFP.png")

p_density_Tet.est_BFP_all_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.est_BFP_all_plot.png")

p_density_Tet.est_BFP_same_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.est_BFP_same_plot.png")

p_density_Tet.est_BFP_lincoln
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.est_BFP_lincoln.png")

p_density_Tet.est_GFP_all_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.est_GFP_all_plot.png")

p_density_Tet.est_GFP_same_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.est_GFP_same_plot.png")

p_density_Tet.est_GFP_lincoln
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.est_GFP_lincoln.png")

p_violin_Tet.cup_BFP_RFP
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="violin_Tet.cup_BFP_RFP.png")

p_density_Tet.cup_BFP_all_plots
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup_BFP_all_plots.png")

p_density_Tet.cup_BFP_same_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup_BFP_same_plot.png")

p_density_Tet.cup_BFP_lincoln
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup_BFP_lincoln.png")

p_density_Tet.cup_RFP_all_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup_RFP_all_plot.png")

p_density_Tet.cup_RFP_same_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup_RFP_same_plot.png")

p_density_Tet.cup_RFP_lincoln
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup_RFP_lincoln.png")

p_violin_Tet.cup.est
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="violin_Tet.cup.est.png")

p_density_Tet.cup.est_BFP_all_plots
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup.est_BFP_all_plots.png")

p_density_Tet.cup.est_BFP_same_plots
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup.est_BFP_same_plots.png")

p_density_Tet.cup.est_BFP_lincoln
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup.est_BFP_lincoln.png")

p_density_Tet.cup.est_RFP_all_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup.est_RFP_all_plot.png")

p_density_Tet.cup.est_RFP_same_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup.est_RFP_same_plot.png")

p_density_Tet.cup.est_RFP_lincoln
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup.est_RFP_lincoln.png")

p_density_Tet.cup.est_GFP_all_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup.est_GFP_all_plot.png")

p_density_Tet.cup.est_GFP_same_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup.est_GFP_same_plot.png")

p_density_Tet.cup.est_GFP_lincoln
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_Tet.cup.est_GFP_lincoln.png")





ggsave(path ="../Docs/" ,filename="plot.png")



```





