---
title: "Guava1plasmid_tidyResults"
author: "Edwin Eliasson"
date: "10/14/2021"
output: html_document
---


## Load libraries
```{r, echo=FALSE}
library(flowCore)
library(tidyverse)
library(viridis)
library(hrbrthemes)
library(hexbin)
library(data.table)
library(ggpubr)

library(ggplot2)
library(ggridges)

filter = dplyr::filter
select = dplyr::select
```

## Load data

All data is in csv format in the "../data/2021-08-27_at_08-43-55am" folder
```{r,warning=FALSE}
filenames = list.files(path = "../data/2021-08-27_at_08-43-55am",full.names = T)

# Extract plate position from filename
plate_pos = filenames %>% gsub(".CSV","",.) %>% gsub(".*am.","",.)

# Loop through and merge all files into a big tibble
tbl = tibble()
for (i in 1:length(filenames)) {
  tbl_file = fread(filenames[i]) %>% mutate(POS = plate_pos[i])
  tbl = rbind(tbl,tbl_file)
}
rm(tbl_file)
```

## Pre-procesing

Replacement of hypgen (-) in columns
```{r}
names(tbl) <- gsub("\\-",".", names(tbl))
glimpse(tbl)
```
## Filter out cells with negative intensity and log transform
```{r}
tbl =
  tbl %>% 
  filter(GRN.B.HLog > 0) %>%
  filter(RED.R.HLog > 0) %>%
  filter(FSC.HLin > 100) 

```


Convert into tidy tibble and add channel info
```{r}
tbl_tidy =
  tbl %>% 
  pivot_longer(-c(POS,TIME),names_to = "CHANNEL",values_to = "INTENSITY") %>% 
  mutate(SCALE = ifelse(grepl("Lin",CHANNEL),"lin","log")) %>% 
  filter(CHANNEL != "RED.R.W")

glimpse(tbl_tidy)
```

Format meta data
```{r}
tbl_meta = 
  fread(file = "../data/plate_map.csv") %>% 
  mutate(DOSE = as.character(DOSE))
```


Merge meta data with flow cytometry data
```{r}
tbl_tidy =
  tbl_tidy %>% 
  full_join(tbl_meta,by = "POS")

head(tbl_tidy)
```

Matrix with flipped columnes
```{r}
tbl_red_green =

tbl_tidy %>% 
  filter(CHANNEL %in% c("FSC.HLog","GRN.B.HLog", "RED.R.HLog")) %>% 
  pivot_wider(names_from = CHANNEL,values_from = INTENSITY)
  

```




### RFP or Coppar plots ###



Violin plot RFP o Copper
```{r}

p_violin_cup_RPF =
  tbl_red_green %>% 
  filter( INDUCER == c("Cup1","None")) %>% 
  mutate(DOSE = factor(DOSE,levels = c("0","1","10","50","100"),ordered = TRUE)) %>%
  ggplot(aes(x = DOSE, y = RED.R.HLog, color = DOSE, fill = DOSE)) +
  geom_violin(alpha = 0.5, adjust = 0.0001,draw_quantiles = 0.5) +
  facet_wrap(vars(CASE_CTRL),ncol = 10) +
  scale_color_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  stat_compare_means(ref.group = "0",label = "p.signif") +
  ggtitle("Violin plot of RFP intensity - Copper plasmid") +
  xlab("Copper (µM)") +
  ylab("RFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_violin_cup_RPF

```


RFP expression depending of CUP conc.
```{r}
p_density_cup_RFP_all_diff_plot =
  tbl_red_green %>% 
  filter(STRAIN == c("CUP")) %>% 
  mutate(DOSE = factor(DOSE,levels = c("0","1","10","50","100"),ordered = TRUE)) %>%
  ggplot(aes(RED.R.HLog, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  facet_wrap(vars(DOSE, INDUCER),nrow = 2) +
  scale_color_viridis(name = "DOSE (µM)", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM)", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  ggtitle ("Density plots for RFP expression - Copper plasmid") +
  ylab("Density") + 
  xlab("RFP Intesity (a.u.)") +
  theme(aspect.ratio = 1,plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_cup_RFP_all_diff_plot
```

ONE PLOT of RFP expression depending of CUP conc
```{r}
p_density_cup_RFP_all_same_plot =
 tbl_red_green %>% 
  filter(STRAIN == c("CUP")) %>% 
  mutate(DOSE = factor(DOSE,levels = c("0","1","10","50","100"),ordered = TRUE)) %>%
  ggplot(aes(RED.R.HLog, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  scale_color_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  ggtitle("Density plots for RFP expression - Copper plasmid") +
  ylab("Density") +
  xlab("RFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_cup_RFP_all_same_plot 
```


LINCOLN RFP expression depending of CUP
```{r}
p_density_cup_RFP_lincoln =
 tbl_red_green %>% 
  filter(STRAIN == c("CUP")) %>% 
  mutate(DOSE = factor(DOSE,levels = c("0","1","10","50","100"),ordered = TRUE)) %>%
  ggplot(lincoln_weather, mapping = aes(x = RED.R.HLog, y = DOSE, fill = stat(x))) +
  geom_density_ridges_gradient(alpha = 0.1, adjust = 0.0001, scale = 3, rel_min_height = 0.01)  +
  #scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis_c(name = "Intesity (a.u.)", option = "magma") +
  theme_bw() +
  ggtitle("Density plots for RFP expression - Copper plasmid") +
  ylab("DOSE (µM)") +
  xlab("RFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5,face = "bold", size = 15))

p_density_cup_RFP_lincoln
```



### GFP or Estradiol Plots ###



Violin plot, not as nice as the one above!
```{r}
p_violin_est_GPF =
  tbl_red_green %>% 
  filter( INDUCER == c("Estradiol","None")) %>% 
  ggplot(aes(x = DOSE, y = GRN.B.HLog, color = DOSE, fill = DOSE)) +
  geom_violin(alpha = 0.5, adjust = 0.5,draw_quantiles = 0.5) +
  facet_wrap(vars(CASE_CTRL),ncol = 10) +
  scale_color_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM)", discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  stat_compare_means(ref.group = "0",label = "p.signif") +
  ggtitle("Violin plot of GFP intensity - Estradiol plasmid") +
  xlab("Estradiol (µM)") +
  ylab("GRP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_violin_est_GPF
```


GFP expression depending of Estradiol conc.
```{r}
p_density_est_GPF_all_diff_plot =
  tbl_red_green %>% 
  filter(STRAIN == c("Estradiol")) %>% 
  ggplot(aes(GRN.B.HLog, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  facet_wrap(vars(DOSE, INDUCER),nrow = 2) +
  scale_color_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  ggtitle ("Density plots for GFP expression - Estradiol plasmid") +
  ylab("Density") + 
    xlab("GFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_est_GPF_all_diff_plot
```


ONE PLOT of GFP expression depending of EsT conc
```{r}

p_density_est_GFP_same_plot =
 tbl_red_green %>% 
  filter(STRAIN == c("Estradiol")) %>% 
  ggplot(aes(GRN.B.HLog, color = DOSE, fill = DOSE)) +
  geom_density(alpha = 0.5, adjust = 0.0001) +
  scale_color_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(name = "DOSE (µM)",discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  ggtitle("Density plots for GFP expression - Estradiol plasmid") +
  ylab("Density") +
  xlab("GFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5, face = "bold", size = 15))

p_density_est_GFP_same_plot

```

LINCOLN GFP expression depending of EST
```{r}
p_density_est_GFP_lincoln =
 tbl_red_green %>% 
  filter(STRAIN == c("Estradiol")) %>% 
  ggplot(lincoln_weather, mapping = aes(x = GRN.B.HLog, y = DOSE, fill = stat(x))) +
  geom_density_ridges_gradient(alpha = .1, adjust = 0.0001, scale = 3, rel_min_height = 0.01) +
  #scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis_c(name = "Intesity (a.u.)", option = "magma") +
  theme_bw() +
  ggtitle("Density plots for GFP expression - Estradiol plasmid") +
  ylab("DOSE (µM)") +
  xlab("GFP Intesity (a.u.)") +
  theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.5,face = "bold", size = 15))

p_density_est_GFP_lincoln

```



```{r}

p_violin_cup_RPF
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="violin_cup_RPF.png")

p_density_cup_RFP_all_diff_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_cup_RFP_all_diff_plot.png")

p_density_cup_RFP_all_same_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_cup_RFP_all_same_plot.png")

p_density_cup_RFP_lincoln
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_cup_RFP_lincoln.png")

p_violin_est_GPF
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="violin_est_GPF.png")

p_density_est_GPF_all_diff_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_est_GPF_all_diff_plot.png")

p_density_est_GFP_same_plot
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_est_GFP_same_plot.png")

p_density_est_GFP_lincoln
ggsave(path ="/Users/Edwin/Google Drive/CHALMERS/iGEM/WetLAB/All_plots/",filename ="density_est_GFP_lincoln.png")


#ggsave(path ="../Docs/" ,filename="plot.png")



```



```{r}
save_plot[[test_]] = ggplot(...)
```





